---
title: "Notebook 4: Spatial Querying"
output:
  html_document:
    toc: true
    toc_depth: 2
editor_options: 
  markdown: 
    wrap: 72
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(message = FALSE, warning = FALSE)
```

## What this notebook does

The Domain API understands suburb names. But urban research often works
with ABS boundaries (SA2, LGA, Greater Capital City regions) that do not
align neatly with suburb names. An SA2 may cover parts of several
suburbs. A suburb may straddle two SA2 boundaries. Querying suburb by
suburb introduces extra costs, gaps and overlaps.

The API's solution is `geoWindow`: you feed the API a polygon as a list
of coordinates and ask for all listings whose property location falls
inside it.

## Why spatial querying is the recommended approach

For any study area larger than a single suburb, spatial querying is
almost always the most credit-efficient approach.

When querying suburb by suburb, every suburb costs at least one probe
credit plus one credit per page of results. Ten suburbs means ten probes
and ten separate sets of fetch pages. A polygon covering the same ten
suburbs costs **one probe and one set of fetch pages for the entire
area**, the same structure as a single-suburb query, regardless of how
many suburb boundaries sit inside it.

The suburb-by-suburb approach from Notebook 3 is still useful when you
specifically want per-suburb breakdowns, or when your study area is
defined by a list of suburb names rather than a geographic boundary. For
everything else, SA2s, LGAs, catchment areas, corridor studies, a
polygon query is the right starting point.

This notebook teaches you:

1.  What GeoJSON boundary files are and where the pre-prepared ones
    live.
2.  Why the coordinate format in GeoJSON files must be converted before
    sending to the API.
3.  The difference between a bounding box (rough rectangle) and a
    polygon (exact boundary), and when to use each.
4.  How to run a spatial listing search and visualise the results on a
    map.
5.  How cursor advancement (from Notebook 3) applies equally to spatial
    queries.

**By the end** you will have downloaded listings for the
Fitzroy/Collingwood area using a precise polygon boundary and produced a
map showing where those listings sit.

------------------------------------------------------------------------

## Before You Start

**If you have already completed Notebook 0**, your packages, `.env`
file, and connection are already set up.

If this is your first time using Domain API, complete
`notebook-0-getting-started.Rmd` first. It covers package installation,
creating the `.env` credentials file, and making a test call to confirm
your connection works. Then complete Notebook 1 before this one, as it
introduces the listings endpoint used throughout this notebook. If you
plan to query a large area (with more than 1,000 listings potentially),
read Notebook 3 first for the cursor advancement technique.

### Set your boundary file path

This notebook uses a GeoJSON boundary file. Set the path to wherever the
file lives on your machine in the setup chunk below. If you are working
from the AURIN training materials repository, an example file is
provided in the `test_areas` folder, but the path is not assumed, set it
explicitly.

Depending on the operating system you are using, copying and pasting a
path directly may cause an error. Windows file manager gives you
backslashes (`C:\Users\you\boundaries\area.geojson`), while Mac and
Linux give you forward slashes (`/Users/you/boundaries/area.geojson`). A
single backslash has a special meaning inside quotes in R, so either
double each one (`"C:\\Users\\you\\boundaries\\area.geojson"`) or swap
them for forward slashes (`"C:/Users/you/boundaries/area.geojson"`),
which R understands on every operating system.

------------------------------------------------------------------------

## Key Terms

**GeoJSON:** A standard file format for storing geographic shapes
(points, lines, polygons) as text. The ABS publishes its SA2, LGA, and
other boundary files in this format.

**Polygon:** A closed shape defined by a list of coordinates (corner
points). A suburb boundary or SA2 boundary is stored as a polygon.

**Coordinate:** A pair of numbers that specifies a location on Earth.
The first number is longitude (east-west position) and the second is
latitude (north-south position). Melbourne is roughly at latitude -37.8
and longitude 144.9.

**Bounding box:** The smallest rectangle that fully encloses a polygon,
defined by its northernmost, southernmost, easternmost, and westernmost
points. It is faster to compute than the full polygon but captures a
larger area.

**SA2 (Statistical Area Level 2):** An ABS geographic unit containing
roughly 3,000 to 25,000 people, used for census and demographic data.

**geoWindow:** The parameter name in the Domain API for spatial
filtering. It accepts either a polygon or a bounding box.

------------------------------------------------------------------------

## Setup: Check Packages and Files

Run the chunk below to confirm all required packages are installed and
your boundary file is found.

```{r package-check}
# Check required packages
needed <- c("httr2", "jsonlite", "purrr", "tibble", "dplyr", "readr", "leaflet")
missing <- needed[!vapply(needed, requireNamespace, logical(1), quietly = TRUE)]

if (length(missing) > 0) {
  cat("Missing packages, run in the R console:\n")
  cat("  install.packages(c(", paste0('"', missing, '"', collapse = ", "), "))\n", sep = "")
} else {
  cat("Packages: OK\n")
}

# -----------------------------------------------------------------------
# Set the path to your GeoJSON boundary file here.
# This can be an absolute path or relative to the location of this notebook.
# Use forward slashes (/) on Mac and Linux. On Windows, use either forward
# slashes or doubled backslashes (\\), because a pasted Windows path with
# single backslashes will not work here.
# -----------------------------------------------------------------------
FITZROY_COLLINGWOOD <- file.path("..", "..", "test_areas", "fitzroy_collingwood.geojson")
# -----------------------------------------------------------------------

if (file.exists(FITZROY_COLLINGWOOD)) {
  cat("Fitzroy/Collingwood boundary: Found  (", normalizePath(FITZROY_COLLINGWOOD), ")\n", sep = "")
} else {
  cat("Fitzroy/Collingwood boundary: NOT FOUND\n")
  cat("  Expected at: ", file.path(normalizePath("."), FITZROY_COLLINGWOOD), "\n", sep = "")
  cat("  Update the path at the top of this chunk.\n")
}
```

## Setup: Connect to the API

```{r connect}
library(dplyr)
library(tibble)
library(purrr)
library(leaflet)

source("utils.R")

tracker <- make_tracker()

cat("Connected to:", PROXY_BASE, "\n")
cat("Account:     ", AURIN_USERNAME, "\n")
```

------------------------------------------------------------------------

## Credit Comparison: Suburb-by-Suburb vs. Polygon

Before getting into the mechanics, it helps to see the credit saving in
concrete numbers using the same 10 inner-Melbourne suburbs from Notebook
3.

The suburb-by-suburb approach sends one probe per suburb, 10 API calls.
A single bounding box covering the same area costs 1 API call. The
saving carries through to the full fetch too: each suburb also needs its
own set of page calls, while a polygon retrieves the entire area in one
continuous run.

**This chunk costs 11 credits total.** If you want to save credits, read
the output and move on, you do not need to re-run it. If you are
planning a large extraction, use the [Credit Calculator
guide](../phase-1/03-credit-calculator.md) to estimate costs before
running.

```{r credit-comparison}
# --- Approach 1: one probe per suburb (10 credits) ---
SUBURBS_NB3 <- list(
  list("Carlton",     "VIC", "3053"),
  list("Fitzroy",     "VIC", "3065"),
  list("Collingwood", "VIC", "3066"),
  list("Richmond",    "VIC", "3121"),
  list("Brunswick",   "VIC", "3056"),
  list("Northcote",   "VIC", "3070"),
  list("Abbotsford",  "VIC", "3067"),
  list("Prahran",     "VIC", "3181"),
  list("St Kilda",    "VIC", "3182"),
  list("South Yarra", "VIC", "3141")
)

START_DATE    <- "2022-01-01"
# Start with an explicitly numeric vector. An empty c() is NULL; assigning
# named values to NULL with [[ ]] creates a list, which sum() cannot add.
suburb_counts <- integer(0)
calls_before  <- tracker$total()

for (entry in SUBURBS_NB3) {
  suburb   <- entry[[1]]
  state    <- entry[[2]]
  postcode <- entry[[3]]

  payload <- list(
    listingType = "Sold",
    listedSince = START_DATE,
    locations = list(list(state = state, suburb = suburb, postCode = postcode,
                          includeSurroundingSuburbs = FALSE))
  )
  count <- probe_count(payload, tracker)
  suburb_counts[[suburb]] <- if (is.null(count)) 0L else count
  cat(sprintf("  %-15s %6s records\n", suburb, format(suburb_counts[[suburb]], big.mark = ",")))
}

suburb_probe_calls <- tracker$total() - calls_before
suburb_total       <- sum(suburb_counts)
tracker$checkpoint("Credit comparison: suburb probes (10 calls)")

cat("\nSuburb-by-suburb:  ", suburb_probe_calls, " probe credits  ->  ",
    format(suburb_total, big.mark = ","), " records total\n", sep = "")

# --- Approach 2: one bounding box covering the same area (1 credit) ---
# Approximate bounding box for the 10 inner-Melbourne suburbs above
inner_melb_box_payload <- list(
  listingType = "Sold",
  listedSince = START_DATE,
  geoWindow = list(
    box = list(
      topLeft     = list(lat = -37.755, lon = 144.940),
      bottomRight = list(lat = -37.875, lon = 145.025)
    )
  )
)

calls_before     <- tracker$total()
bbox_count       <- probe_count(inner_melb_box_payload, tracker)
bbox_probe_calls <- tracker$total() - calls_before
tracker$checkpoint("Credit comparison: bounding box probe (1 call)")

cat("Single bounding box: ", bbox_probe_calls, " probe credit   ->  ",
    format(bbox_count, big.mark = ","), " records total\n\n", sep = "")

savings <- suburb_probe_calls - bbox_probe_calls
cat(sprintf("Probe credits saved: %d of %d (%.0f%% reduction)\n",
            savings, suburb_probe_calls, savings / suburb_probe_calls * 100))
cat("\n")
cat("Note: the bounding box count may be slightly higher because the rectangle\n")
cat("extends a little beyond some suburb edges, capturing neighbouring properties.\n")
```

------------------------------------------------------------------------

## What Is a GeoJSON File?

GeoJSON is a text file format for storing geographic shapes. Open any
`.geojson` file in a text editor and you will see something like:

``` json
{"type": "FeatureCollection", "features": [{"geometry": {"coordinates": [[144.97, -37.80]]}}]}
```

Each pair of numbers is one corner point of the boundary polygon. The
ABS publishes boundary files in this format for SA2, LGA, and other
boundaries, you can download them from the ABS website or use your own.

The chunks below use `FITZROY_COLLINGWOOD`, a small inner-Melbourne area
used as the worked example. To use your own boundary, update the path in
the setup chunk and replace `FITZROY_COLLINGWOOD` with your variable
name in the chunks below.

### Load and inspect the Fitzroy/Collingwood boundary

Run the chunk below to open the file and print its contents. You do not
need to understand all of it; just notice that coordinates come in pairs
and that the numbers look like Melbourne longitude/latitude values.

```{r inspect-geojson}
# Open the GeoJSON file and read its contents.
# read_json turns the text file into a nested R list.
fitzroy_geojson <- jsonlite::read_json(FITZROY_COLLINGWOOD, simplifyVector = FALSE)

# Get the geometry (the boundary shape) of the first feature in the file
feature <- fitzroy_geojson$features[[1]]
geom    <- feature$geometry

# Get the outer ring of the polygon (the boundary itself, not any holes inside it)
ring <- geom$coordinates[[1]]

cat("Boundary type:", geom$type, "\n")
cat("Number of corner points:", length(ring), "\n\n")
cat("First 3 coordinate pairs (GeoJSON format: [longitude, latitude]):\n")
for (coord in head(ring, 3)) {
  cat(sprintf("  [lon=%.6f, lat=%.6f]\n", coord[[1]], coord[[2]]))
}
```

------------------------------------------------------------------------

## The Coordinate Order Problem

GeoJSON stores coordinates as `[longitude, latitude]`, with longitude
first. The Domain API expects `lat` and `lon` as named fields, with
latitude first.

If you send coordinates in the wrong order, the polygon will be placed
somewhere in the Indian Ocean. The API will not warn you, it will simply
return zero results, and the probe credit is spent.

The `geojson_file_to_api_polygon()` function handles the conversion
automatically. But if you ever build coordinates manually or load them
from a different source, the swap is easy to introduce silently.

`validate_australia_coords()` is a zero-credit guard from `utils.R` that
checks whether your converted points fall within Australia's bounding
box before you make any API call. The chunk below the conversion
demonstrates it on both correct and swapped coordinates.

```{r convert-coords}
# Convert the GeoJSON file to the format the Domain API expects
api_polygon <- geojson_file_to_api_polygon(FITZROY_COLLINGWOOD)

cat("Number of polygon points for the API:", length(api_polygon), "\n\n")
cat("First 3 points after conversion (API format: lat, lon):\n")
for (pt in head(api_polygon, 3)) {
  cat(sprintf("  lat=%.6f, lon=%.6f\n", pt$lat, pt$lon))
}
cat("\nCompare: the lat and lon values are the same but the order is now lat-first.\n")

# This is the complete geoWindow payload structure ready to send to the API
polygon_geo_window <- list(polygon = list(points = api_polygon))
```

```{r validate-coords}
# validate_australia_coords is defined in utils.R and available after source().
# Run it after any coordinate conversion and before the first probe.

# --- correct coordinates (should pass) ---
cat("=== Correct coordinates (after conversion) ===\n")
validate_australia_coords(api_polygon, label = "Fitzroy/Collingwood polygon")

# --- swapped coordinates (GeoJSON order sent directly) ---
cat("\n=== Swapped coordinates (GeoJSON [lon, lat] sent as-is) ===\n")
swapped <- lapply(api_polygon, \(pt) list(lat = pt$lon, lon = pt$lat))
result  <- validate_australia_coords(swapped, label = "Fitzroy/Collingwood polygon (swapped)")
# result is FALSE when coordinates fail the check; the warning above explains what to fix
```

------------------------------------------------------------------------

## Bounding Box vs. Polygon: Which Should You Use?

The API supports two spatial filter types:

**Bounding box** (`geoWindow$box`): a rectangle defined by four edges
(north, south, east, west). Think of drawing a rectangle around the
boundary on a map. It is simple to compute but will include listings
from outside your actual study area. Any property in the corners of the
rectangle but outside the true boundary will be captured.

**Polygon** (`geoWindow$polygon`): traces the exact boundary. Only
listings whose property coordinates fall inside the polygon are
returned. This is more precise but requires sending more coordinates in
each request.

**Rule of thumb:** use the polygon for official boundaries (SA2, LGA)
where precision matters. Use the bounding box for quick exploratory
queries or for very irregular shapes with hundreds of vertices (where
the polygon payload becomes very large).

### Compute the bounding box

The `geojson_bbox_to_api_box()` function finds the northernmost,
southernmost, easternmost, and westernmost points of the polygon.

```{r compute-bbox}
# Compute the bounding box of the Fitzroy/Collingwood polygon
api_box <- geojson_bbox_to_api_box(FITZROY_COLLINGWOOD)

cat("Bounding box corners:\n")
cat(sprintf("  North edge (topLeft lat):     %.6f\n", api_box$topLeft$lat))
cat(sprintf("  South edge (bottomRight lat): %.6f\n", api_box$bottomRight$lat))
cat(sprintf("  West edge  (topLeft lon):     %.6f\n", api_box$topLeft$lon))
cat(sprintf("  East edge  (bottomRight lon): %.6f\n", api_box$bottomRight$lon))

# This is the complete geoWindow payload for the bounding box
box_geo_window <- list(box = api_box)
```

### Compare the record counts: bounding box vs. polygon

The next chunk runs a 1-credit probe for each approach. **This costs 2
credits total.** The difference in counts is the number of listings
captured by the rectangle's corners that fall outside the true polygon
boundary.

Note: the test boundary file used in this notebook is a simple rectangle
(5 points), so the tight bounding box computed above is identical to the
polygon and would return the same count, which defeats the purpose of
the demonstration. To illustrate the difference clearly, the comparison
below uses a deliberately padded bounding box that extends 0.015 degrees
beyond each edge of the polygon, making it meaningfully larger than the
true boundary.

```{r compare-bbox-polygon}
# Define the base search criteria (same for both approaches)
base_criteria <- list(
  listingType = "Sold",
  listedSince = "2021-01-01"
)

# Padded bounding box: extends 0.015 degrees beyond each edge of the polygon.
# This is deliberate: the tight bbox computed from a rectangular polygon is
# identical to the polygon itself, so padding is needed to show a meaningful difference.
PAD <- 0.015
padded_box_geo_window <- list(
  box = list(
    topLeft     = list(lat = api_box$topLeft$lat     + PAD,
                       lon = api_box$topLeft$lon     - PAD),
    bottomRight = list(lat = api_box$bottomRight$lat - PAD,
                       lon = api_box$bottomRight$lon + PAD)
  )
)

# Probe with padded bounding box (1 credit)
payload_box <- modifyList(base_criteria, list(geoWindow = padded_box_geo_window))
count_box   <- probe_count(payload_box, tracker)
tracker$checkpoint("Bounding box probe")

# Probe with polygon (1 credit)
payload_polygon <- modifyList(base_criteria, list(geoWindow = polygon_geo_window))
count_polygon   <- probe_count(payload_polygon, tracker)
tracker$checkpoint("Polygon probe")

cat("Padded bounding box count:", format(count_box,     big.mark = ","), "\n")
cat("Polygon count:            ", format(count_polygon, big.mark = ","), "\n")

if (!is.null(count_box) && !is.null(count_polygon)) {
  overshoot <- count_box - count_polygon
  cat("Overshoot:", format(overshoot, big.mark = ","),
      "extra listings captured by the box but outside the true boundary\n")
}
```

**Reading the result:** the padded bounding box returns more listings
than the polygon because it extends beyond the true boundary. Those
extra listings belong to neighbouring streets and suburbs caught by the
rectangle's edges. With a real SA2 or LGA boundary (which has an
irregular shape), the tight bounding box would also produce overshoot,
often substantial in areas with irregular coastlines or diagonal edges.
For a precise study, always use the polygon.

------------------------------------------------------------------------

## Fetching Listings Within the Polygon

The probe showed over 3,500 records for the Fitzroy/Collingwood polygon
since 2021, so cursor advancement is needed. The `fetch_all_cursor`
function below is the same one introduced in Notebook 3, the only
difference from a suburb-based query is that the payload uses
`geoWindow` instead of `locations`. The function itself is identical.

**Note on credits:** each page of 200 records costs 1 credit. The chunk
below will spend roughly 18 to 20 credits to fetch the full dataset.

```{r fetch-polygon}
fetch_all_cursor <- function(base_payload, start_date, page_size = 200, tracker) {
  # Retrieve ALL listings for a query that may exceed 1,000 results.
  # Works with both suburb-based and spatial (geoWindow) queries.

  all_listings  <- list()
  current_since <- start_date
  prev_cursor   <- NULL
  run           <- 0

  repeat {
    run   <- run + 1
    page  <- 1
    batch <- list()
    hit_limit <- FALSE

    repeat {
      payload <- modifyList(base_payload, list(
        listedSince = current_since,
        sort        = list(sortKey = "DateListed", direction = "Ascending"),
        pageSize    = page_size,
        pageNumber  = page
      ))

      r <- tracker$post(
        paste0(PROXY_BASE, "/v1/listings/residential/_search"),
        json_body = payload
      )

      if (resp_status(r) == 400 && grepl("Cannot page beyond 1000", resp_body_string(r))) {
        hit_limit <- TRUE
        break
      }
      if (resp_status(r) != 200) {
        cat("  Run ", run, ", page ", page, ": HTTP ", resp_status(r), "\n", sep = "")
        return(unname(all_listings))
      }

      groups <- resp_body_json(r, simplifyVector = FALSE)
      for (g in groups) {
        raw <- g$listings
        if (is.null(raw) || length(raw) == 0) raw <- g$listing
        if (is.null(raw) || length(raw) == 0) next
        if (is.null(names(raw))) batch <- c(batch, raw) else batch <- c(batch, list(raw))
      }

      hdr <- resp_header(r, "x-pagination-pagesize")
      actual_page_size <- if (is.null(hdr)) page_size else as.integer(hdr)
      if (length(groups) < actual_page_size) break
      page <- page + 1
    }

    before <- length(all_listings)
    for (item in batch) {
      id <- field(item, "id")
      if (!is.na(id)) all_listings[[as.character(id)]] <- item
    }
    cat(sprintf("  Run %d: +%5d new | total: %6d\n",
                run, length(all_listings) - before, length(all_listings)))

    if (!hit_limit || length(batch) == 0) break

    dates <- vapply(batch, \(item) substr(field(item, "dateListed"), 1, 10), character(1))
    dates <- dates[!is.na(dates)]
    if (length(dates) == 0) break
    cursor <- max(dates)
    if (!is.null(prev_cursor) && cursor == prev_cursor) {
      cat("  Cursor stuck at ", cursor, ". Stopping.\n", sep = "")
      break
    }
    prev_cursor   <- cursor
    current_since <- cursor
  }

  unname(all_listings)
}


cat("Fetching Fitzroy/Collingwood polygon listings (cursor advancement)...\n")
polygon_raw <- fetch_all_cursor(payload_polygon, start_date = "2021-01-01",
                                tracker = tracker)
tracker$checkpoint("Polygon fetch")

# Extract coordinates and key fields, keeping only records that have coordinates
df_polygon <- polygon_raw |>
  map(\(item) tibble(
    id          = as.character(field(item, "id")),
    suburb      = field(item, "propertyDetails", "suburb"),
    lat         = as.numeric(field(item, "propertyDetails", "latitude")),
    lon         = as.numeric(field(item, "propertyDetails", "longitude")),
    date_listed = substr(field(item, "dateListed"), 1, 10)
  )) |>
  bind_rows() |>
  filter(!is.na(lat), !is.na(lon))

cat("\nListings with coordinates:", format(nrow(df_polygon), big.mark = ","), "\n")
knitr::kable(head(df_polygon, 5))
```

------------------------------------------------------------------------

## Visualising the Difference: Polygon vs. Bounding Box

The map below plots the listings already fetched (`df_polygon`) over an
OpenStreetMap base layer, with both boundaries drawn on top:

-   **Blue line**: the polygon boundary (the true study area)
-   **Red line**: the padded bounding box (extends beyond the polygon in
    all directions)
-   **Blue dots**: listings returned by the polygon query

You can see visually that the red box extends into neighbouring streets
and suburbs. Any properties in that fringe would be captured by a
bounding box query but not a polygon query.

```{r map}
centre_lat <- (api_box$topLeft$lat + api_box$bottomRight$lat) / 2
centre_lon <- (api_box$topLeft$lon + api_box$bottomRight$lon) / 2

# Pull the polygon's coordinates out into plain vectors for leaflet
poly_lats <- vapply(api_polygon, \(pt) pt$lat, numeric(1))
poly_lons <- vapply(api_polygon, \(pt) pt$lon, numeric(1))

tl <- padded_box_geo_window$box$topLeft
br <- padded_box_geo_window$box$bottomRight

m <- leaflet() |>
  addTiles() |>
  setView(lng = centre_lon, lat = centre_lat, zoom = 14) |>

  # Polygon boundary (blue)
  addPolygons(
    lng = poly_lons, lat = poly_lats,
    color = "blue", weight = 2, fill = FALSE,
    label = "Polygon boundary"
  ) |>

  # Padded bounding box boundary (red)
  addRectangles(
    lng1 = tl$lon, lat1 = tl$lat,
    lng2 = br$lon, lat2 = br$lat,
    color = "red", weight = 2, fill = FALSE,
    label = "Padded bounding box"
  )

# Listings from the polygon fetch (blue dots)
if (nrow(df_polygon) > 0) {
  m <- m |>
    addCircleMarkers(
      data = df_polygon, lng = ~lon, lat = ~lat,
      radius = 3, color = "steelblue", stroke = FALSE, fillOpacity = 0.5
    )
}

m
```

------------------------------------------------------------------------

## What If Something Goes Wrong?

**Boundary file not found:** Update the `FITZROY_COLLINGWOOD` path in
the setup chunk to the actual location of your file. The message prints
the full path it tried so you can see exactly what to correct. If you
pasted the path from Windows file manager, replace each single backslash
with a forward slash (`/`) or a doubled backslash (`\\`), otherwise R
cannot read it.

**Probe returns 0 records from the polygon:** This usually means the
coordinates are in the wrong order (longitude and latitude swapped). The
`geojson_file_to_api_polygon()` function handles the conversion
automatically, so this should not happen if you use it. If you provide
your own coordinates manually, double-check the order and run
`validate_australia_coords()` before the first probe.

**The map shows dots in the wrong location (e.g. the ocean):** Longitude
and latitude may have been swapped somewhere. Melbourne is at roughly
lat=-37.8, lon=144.9. If your dots appear at lat=144.9, lon=-37.8 (which
is in the Indian Ocean), the coordinate order needs to be fixed.

**The map area is blank or the map does not appear:** The `leaflet`
package is probably not installed. Run `install.packages("leaflet")` and
re-run the chunk. If you are reading the `.Rmd` source rather than the
knitted HTML, the map will not render at all; click **Knit** in RStudio
to produce the HTML version, or run the chunk interactively to see the
map in the Viewer pane.

**Authentication failure:** Check your `.env` file and confirm
`AURIN_USERNAME` and `AURIN_PASSWORD` are set correctly. See the [Data
Access Guide](../phase-1/01-data-access-guide.md) if you need to set up
credentials from scratch.

------------------------------------------------------------------------

## You Have Reached the End of Phase 2

You can now query the Domain API by suburb name or by a custom
geographic boundary, and retrieve all matching records regardless of how
many there are.

Here is a summary of what each notebook covered:

-   **Notebook 0:** Setting up your environment and making your first
    API call.
-   **Notebook 1:** The listings endpoint, filtering, pagination, and
    saving results to CSV.
-   **Notebook 2:** The suburb performance statistics endpoint,
    quarterly trends, and charting.
-   **Notebook 3:** Cursor advancement for queries over 1,000 records,
    plus checkpoint recovery for long-running extractions.
-   **Notebook 4 (this notebook):** Spatial queries using GeoJSON
    boundary files.

From here, apply these tools to your own research question. The [Credit
Calculator guide](../phase-1/03-credit-calculator.md) can help you
estimate costs before running a large extraction.

------------------------------------------------------------------------

## Credit Summary

```{r credit-summary}
tracker$summary()
```
