---
title: "Notebook 3: Pagination Tricks"
output:
  html_document:
    toc: true
    toc_depth: 2
editor_options: 
  markdown: 
    wrap: 72
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(message = FALSE, warning = FALSE)
```

## What this notebook covers

Two situations make basic page-by-page fetching from Notebook 1
inadequate:

1.  **More than 1,000 records.** The listings endpoint silently
    truncates results at 1,000. Areas like South Yarra or the inner-city
    ring have far more than 1,000 listings for any multi-year window.
    This notebook solves this by splitting the retrieval into
    overlapping date windows.

2.  **Large multi-suburb extractions.** Fetching 50 suburbs in a single
    run can take 20 to 30 minutes and can consume a significant number
    of credits. If anything goes wrong mid-run, all progress is lost
    without a checkpoint system.

This notebook covers both techniques and shows how to combine them into
a robust extraction loop.

**By the end** you will have run a complete multi-suburb extraction that
can survive interruptions without wasting credits.

------------------------------------------------------------------------

## Before You Start

**Complete Notebooks 0 and 1 before this one.** Notebook 3 builds on the
probe and pagination patterns from Notebooks 0 and 1, and assumes you
are already comfortable with the listings endpoint. Notebook 2 (suburb
statistics) is independent and can be completed before or after this
notebook.

**If you have already completed Notebooks 0 and 1**, your packages,
`.env` file, and connection are already set up.

------------------------------------------------------------------------

## Key Terms

**Cursor:** A marker that tracks your position in a large dataset. When
you cannot page past position 1,000, you move the cursor (your starting
date) forward and start paging again from the new position.

**Cursor advancement:** The technique of repeatedly advancing the
`listedSince` date to step through a dataset that exceeds 1,000 records.

**Deduplication:** Removing duplicate records. Some listings appear in
two consecutive cursor windows because they fall right on the boundary
date. Storing records in a *named list* keyed by listing ID removes them
automatically: assigning the same name twice simply overwrites.

**Checkpoint:** A saved record of how far an operation has progressed,
like hitting Save in a video game. If something fails, you restart from
the last save point, not from the beginning.

**Resume:** Continuing an interrupted operation by loading a checkpoint
and skipping the steps already completed.

**Interrupt:** What R raises when you press the Stop button in RStudio
(or Ctrl+C in a terminal). We catch this to save progress before
stopping.

**CSV file:** A plain-text spreadsheet format that Excel and other tools
can open.

------------------------------------------------------------------------

## Part 1: The 1,000-Record Cap

The listings endpoint returns at most **1,000 records per request**. If
your query matches 4,200 records, you get the first 1,000. The remaining
3,200 are silently dropped, with no error and no warning.

Notebook 1 introduced the density probe: a 1-credit check that tells you
the total count before you download anything. If that count is over
1,000, simple pagination cannot retrieve the full dataset. This section
shows you how to handle it.

### Credit cost per suburb

Each suburb requires one probe credit, then one credit per page of
results (up to 200 records per page):

-   1 to 200 records, **2 credits** (1 probe + 1 page)
-   201 to 400 records, **3 credits** (1 probe + 2 pages)
-   401 to 600 records, **4 credits** (1 probe + 3 pages)
-   and so on

Most inner-city suburbs have several hundred to a few thousand records,
so **3 to 15 credits per suburb** is a typical range. The 10-suburb run
at the end of this notebook spent 218 credits in total.

### Why checkpoints matter

If a 50-suburb run fails halfway through and you have no checkpoint, you
must start over from suburb 1, spending all those credits again. With a
checkpoint, the completed suburbs are skipped and only the remaining
ones are fetched.

| Scenario                                             | Credits spent                           | Credits wasted                         |
|------------------------|------------------------|------------------------|
| 50-suburb run, no failure                            | \~150 to 500 depending on suburb sizes  | 0                                      |
| Failure at suburb 35, restart **without** checkpoint | Double the above                        | \~105+ (suburbs 1 to 35 fetched twice) |
| Failure at suburb 35, restart **with** checkpoint    | \~original cost + suburbs 36 to 50 only | 0                                      |

The monthly credit limit is 1,000. A single failed un-checkpointed run
can waste more than 10% of your monthly budget before you collect any
usable data.

------------------------------------------------------------------------

## Setup: Check Packages

```{r package-check}
needed <- c("httr2", "jsonlite", "purrr", "tibble", "dplyr", "readr")
missing <- needed[!vapply(needed, requireNamespace, logical(1), quietly = TRUE)]

if (length(missing) > 0) {
  cat("Missing packages, run in the R console:\n")
  cat("  install.packages(c(", paste0('"', missing, '"', collapse = ", "), "))\n", sep = "")
} else {
  cat("All packages found. Setup OK.\n")
}
```

## Setup: Connect to the API and Create the Checkpoint Folder

The chunk below also creates a `checkpoints/` folder inside `phase-2/`
where the progress files will be saved. If the folder already exists,
nothing happens.

```{r connect}
library(dplyr)
library(tibble)
library(purrr)
library(readr)

source("utils.R")

tracker <- make_tracker()

# Checkpoints are written to a "checkpoints" folder next to this notebook.
# To use a different folder, give the full path with forward slashes (/) or
# doubled backslashes (\\), since a pasted Windows path with single
# backslashes may not work.
CHECKPOINT_DIR <- "checkpoints"
dir.create(CHECKPOINT_DIR, showWarnings = FALSE)  # showWarnings = FALSE: fine if it exists

CHECKPOINT_FILE <- file.path(CHECKPOINT_DIR, "extraction_checkpoint.json")

cat("Connected to:", PROXY_BASE, "\n")
cat("Account:     ", AURIN_USERNAME, "\n")
cat("Checkpoint folder:", normalizePath(CHECKPOINT_DIR), "\n")
```

------------------------------------------------------------------------

## Cursor Advancement

When the density probe shows more than 1,000 records, cursor advancement
splits the retrieval into date windows.

Each window fetches up to 1,000 records sorted oldest to newest. When
the cap is hit, `listedSince` advances to the listing date of the last
record in that batch and the fetch restarts from there.

The cursor lands on the last record's date, not the day after, because
multiple listings can share the same date. Any listings dated the same
day as the 1,000th record that did not fit in the batch would be missed
if the cursor skipped ahead by one day. Since we cannot see past the
1,000th record, the last known date is the only safe position.

This means some records near the boundary will be fetched twice. That is
by design: results are stored in a named list keyed by listing ID, so a
duplicate simply overwrites the original and the final dataset stays
clean.

We will demonstrate this on South Yarra 3141 from 2019 onwards, which
has well over 1,000 sold listings.

### Step 1: Confirm the record count

```{r probe-south-yarra}
# Define the South Yarra query for the cursor demonstration
south_yarra_payload <- list(
  listingType = "Sold",
  listedSince = "2019-01-01",
  locations = list(list(
    state    = "VIC",
    suburb   = "South Yarra",
    postCode = "3141",
    includeSurroundingSuburbs = FALSE
  ))
)

# Run a density probe to confirm the count (1 credit)
sy_count <- probe_count(south_yarra_payload, tracker)
tracker$checkpoint("South Yarra probe")

cat("South Yarra 3141 (from 2019): ", format(sy_count, big.mark = ","), " records\n", sep = "")
cat("Exceeds 1,000-record limit:   ", !is.null(sy_count) && sy_count > 1000, "\n")
cat("\n")
cat("Simple pagination would silently miss everything above record 1,000.\n")
cat("Cursor advancement retrieves the complete dataset.\n")
```

### Step 2: Define the cursor function

The `fetch_all_cursor` function below implements cursor advancement. The
comments walk through each stage.

```{r fetch-all-cursor}
fetch_all_cursor <- function(base_payload, start_date, page_size = 200, tracker) {
  # Retrieve ALL listings for a query that may exceed 1,000 results.
  #
  # Uses cursor advancement: repeatedly advances listedSince to step through
  # the full dataset in chunks of up to 1,000. Deduplicates by listing ID.
  #
  # base_payload: the search criteria (suburb, listing type) WITHOUT listedSince.
  # start_date:   the earliest listing date to include (YYYY-MM-DD format).
  # page_size:    records per page (max 200).
  #
  # Returns: a deduplicated list of all listing records.

  all_listings  <- list()   # named by listing ID, so duplicates overwrite themselves
  current_since <- start_date
  prev_cursor   <- NULL
  run           <- 0

  repeat {
    run   <- run + 1
    page  <- 1
    batch <- list()
    hit_limit <- FALSE

    # --- Inner loop: page through this cursor window ---
    repeat {
      payload <- modifyList(base_payload, list(
        listedSince = current_since,
        sort        = list(sortKey = "DateListed", direction = "Ascending"),
        pageSize    = page_size,
        pageNumber  = page
      ))

      r <- tracker$post(
        paste0(PROXY_BASE, "/v1/listings/residential/_search"),
        json_body = payload
      )

      # The API refuses to page past record 1,000. That refusal is the signal
      # to advance the cursor rather than an error to report.
      if (resp_status(r) == 400 && grepl("Cannot page beyond 1000", resp_body_string(r))) {
        hit_limit <- TRUE
        break
      }

      if (resp_status(r) != 200) {
        cat("  Run ", run, ", page ", page, ": unexpected HTTP ",
            resp_status(r), "\n", sep = "")
        return(unname(all_listings))
      }

      groups <- resp_body_json(r, simplifyVector = FALSE)
      for (g in groups) {
        raw <- g$listings
        if (is.null(raw) || length(raw) == 0) raw <- g$listing
        if (is.null(raw) || length(raw) == 0) next
        # An unnamed list is a JSON array of listings; a named list is one listing
        if (is.null(names(raw))) batch <- c(batch, raw) else batch <- c(batch, list(raw))
      }

      hdr <- resp_header(r, "x-pagination-pagesize")
      actual_page_size <- if (is.null(hdr)) page_size else as.integer(hdr)
      if (length(groups) < actual_page_size) break
      page <- page + 1
    }

    # --- Merge this window's batch into the running total ---
    before <- length(all_listings)
    for (item in batch) {
      id <- field(item, "id")
      if (!is.na(id)) all_listings[[as.character(id)]] <- item
    }
    cat(sprintf("  Cursor run %d: +%5d new | total: %6d\n",
                run, length(all_listings) - before, length(all_listings)))

    # If we never hit the cap, this window held everything left. Done.
    if (!hit_limit || length(batch) == 0) break

    # --- Advance the cursor to the latest listing date we saw ---
    dates <- vapply(batch, \(item) substr(field(item, "dateListed"), 1, 10), character(1))
    dates <- dates[!is.na(dates)]
    if (length(dates) == 0) break

    # Dates are YYYY-MM-DD strings, so the alphabetical maximum is also the latest date
    cursor <- max(dates)

    # If the cursor cannot move, every record in the window shares one date and
    # we would loop forever. Stop and say so rather than spending credits silently.
    if (!is.null(prev_cursor) && cursor == prev_cursor) {
      cat("  Cursor stuck at ", cursor,
          " -- stopping. Some records near this date may be missed.\n", sep = "")
      break
    }

    prev_cursor   <- cursor
    current_since <- cursor
  }

  unname(all_listings)
}

cat("fetch_all_cursor defined.\n")
```

### Step 3: Fetch all South Yarra listings

The chunk below runs the full extraction. Each cursor window fetches up
to 1,000 records across up to 5 pages of 200 records each, so **one
cursor window costs up to 5 credits**. The total depends on how many
records match the query.

**Expected output:** Several lines like "Cursor run 1: +1,000 new \|
total: 1,000", continuing until a final run with fewer than 1,000 new
records.

```{r fetch-south-yarra}
cat("Fetching South Yarra 3141 (cursor advancement)...\n")
south_yarra_raw <- fetch_all_cursor(south_yarra_payload, start_date = "2019-01-01",
                                    tracker = tracker)
tracker$checkpoint("South Yarra cursor fetch")

# A listing's price lives in one of two places depending on listing type
sold_price_of <- function(item) {
  price <- field(item, "soldData", "soldPrice")
  if (is.na(price)) price <- field(item, "priceDetails", "price")
  price
}

# Build a table from the results
df_sy <- south_yarra_raw |>
  map(\(item) tibble(
    id            = as.character(field(item, "id")),
    suburb        = field(item, "propertyDetails", "suburb"),
    property_type = field(item, "propertyDetails", "propertyType"),
    bedrooms      = field(item, "propertyDetails", "bedrooms"),
    date_listed   = substr(field(item, "dateListed"), 1, 10),
    sold_price    = sold_price_of(item)
  )) |>
  bind_rows()

cat("\nSouth Yarra:", format(nrow(df_sy), big.mark = ","), "records fetched.\n")
knitr::kable(head(df_sy, 5))
```

### Step 4: Validate the results

Compare the cursor fetch count against the probe count from Step 1. They
should be close. A small difference (a few records) is normal because
new listings can appear between the probe and the full fetch. A large
difference (more than 10%) suggests the cursor may have got stuck or the
date window was misconfigured.

```{r validate-cursor}
cat(sprintf("Probe count:          %6s\n", format(sy_count,      big.mark = ",")))
cat(sprintf("Cursor fetched count: %6s\n", format(nrow(df_sy),   big.mark = ",")))
cat(sprintf("Difference:           %6s  (a small number is expected)\n",
            format(abs(sy_count - nrow(df_sy)), big.mark = ",")))
cat("\n")

duplicates <- sum(duplicated(df_sy$id))
cat("Duplicate listing IDs:", duplicates, " (expected: 0)\n\n")

cat("Date range covered:\n")
cat("  Earliest listing:", min(df_sy$date_listed, na.rm = TRUE), "\n")
cat("  Latest listing:  ", max(df_sy$date_listed, na.rm = TRUE), "\n")
```

------------------------------------------------------------------------

## Part 2: Checkpoint Recovery

The cursor advancement above retrieves all listings for one suburb. For
a large study covering 50 suburbs, cursor advancement alone is not
enough: if the run fails midway, you lose all progress and must restart
from scratch, spending all those credits again.

The checkpoint pattern saves your progress to disk after each suburb. On
a restart, suburbs already in the checkpoint are skipped without
spending any credits. The sections below define the save and load
functions, wrap cursor advancement into a per-suburb fetcher, and
combine both into a checkpoint-aware extraction loop.

------------------------------------------------------------------------

## What the Checkpoint File Contains

The checkpoint file is a JSON file with three pieces of information:

1.  **`completed`:** a list of suburb labels (e.g. "Carlton 3053") that
    have been fully downloaded. When resuming, any suburb in this list
    is skipped.

2.  **`results`:** all listing records collected so far, stored as a
    named list keyed by listing ID. Using the ID as the name ensures
    that if a suburb is accidentally fetched twice (e.g. because it was
    in progress when a failure occurred), each listing appears only
    once.

3.  **`last_updated`:** the date and time the checkpoint was last
    written.

An example checkpoint file looks like this:

``` json
{
  "completed": ["Carlton 3053", "Fitzroy 3065"],
  "results": {"123456": {"id": "123456"}, "789012": {"id": "789012"}},
  "last_updated": "2026-05-13T14:22:00"
}
```

### Define the save and load functions

The `save_checkpoint()` function writes the current progress to the
checkpoint file. The `load_checkpoint()` function reads it back. Both
are simple: they just convert R data to and from a JSON text file.

Read the comments in the chunk below for a line-by-line explanation.

```{r checkpoint-functions}
save_checkpoint <- function(path, completed, results_list) {
  # path:         the file path to write to.
  # completed:    character vector of suburb labels that are fully done.
  # results_list: named list mapping listing ID to listing record.

  payload <- list(
    # I() tells jsonlite "keep this as a JSON array, even if it has one element".
    # Without it, a single completed suburb would be written as "Carlton 3053"
    # instead of ["Carlton 3053"], and loading it back would break the resume logic.
    completed    = I(completed),
    results      = results_list,
    last_updated = format(Sys.time(), "%Y-%m-%dT%H:%M:%S")
  )

  # write_json converts the R list into a JSON text file
  jsonlite::write_json(payload, path, auto_unbox = TRUE, null = "null", digits = NA)

  cat("    [saved]", length(completed), "suburbs done,",
      format(length(results_list), big.mark = ","), "listings.\n")
}


load_checkpoint <- function(path) {
  # If no checkpoint file exists (first run), returns empty placeholders
  # so the extraction loop can start fresh.
  #
  # Returns a list with two parts: $completed and $results.

  if (file.exists(path)) {  # if a checkpoint file is on disk, load it
    data <- jsonlite::read_json(path, simplifyVector = FALSE)

    # read_json gives back a list of single strings; unlist turns it into a
    # plain character vector, which is what the "already done?" check expects.
    completed <- unlist(data$completed)
    if (is.null(completed)) completed <- character(0)

    results <- if (is.null(data$results)) list() else data$results

    cat("Checkpoint loaded:", length(completed), "suburbs already done,",
        format(length(results), big.mark = ","), "listings.\n")
    cat("Last saved:", if (is.null(data$last_updated)) "unknown" else data$last_updated, "\n")

    list(completed = completed, results = results)
  } else {  # no checkpoint file, start fresh
    cat("No checkpoint file found. Starting from scratch.\n")
    list(completed = character(0), results = list())
  }
}

cat("save_checkpoint and load_checkpoint defined.\n")
```

### Confirm the round-trip works

Before using these functions for real data, the chunk below saves a
small test checkpoint and loads it back. You should see the same data
you saved, confirming that the save and load functions are working
correctly.

```{r checkpoint-roundtrip}
# Save a tiny test checkpoint
test_file <- file.path(CHECKPOINT_DIR, "test_checkpoint.json")
save_checkpoint(
  test_file,
  completed    = c("Carlton 3053"),
  results_list = list("99999" = list(id = "99999", suburb = "Carlton"))
)

# Load it back
loaded <- load_checkpoint(test_file)

cat("\n")
cat("Completed suburbs loaded:", loaded$completed, "\n")
cat("Listing IDs loaded:      ", names(loaded$results), "\n")

# Remove the test file, it was just for demonstration
file.remove(test_file)
cat("\nTest complete. Test file removed.\n")
```

------------------------------------------------------------------------

## The Extraction Functions

The two functions below handle the actual API fetching. You do not need
to understand the internals, just know what each one does:

-   **`fetch_suburb_listings(suburb, state, postcode, start_date)`:**
    downloads all sold listings for one suburb from `start_date`
    onwards. Uses the cursor advancement defined above, so it works
    correctly even for suburbs with more than 1,000 listings. Returns a
    named list mapping listing ID to listing record.

-   **`extract_fields(item)`:** takes one raw listing record (a complex
    nested list) and pulls out the fields you need into a flat row,
    ready to put in a spreadsheet.

Run both chunks to define the functions.

```{r fetch-suburb-listings}
fetch_suburb_listings <- function(suburb, state, postcode, start_date,
                                  listing_type = "Sold", page_size = 200, tracker) {
  # Download all listings for one suburb using cursor advancement.
  #
  # Uses the same cursor technique defined earlier in this notebook, wrapped into
  # a single function call. Works for any number of records, not just under 1,000.
  #
  # Returns a named list mapping listing ID to the full listing record.

  base_payload <- list(
    listingType = listing_type,
    locations = list(list(
      state    = state,
      suburb   = suburb,
      postCode = postcode,
      includeSurroundingSuburbs = FALSE
    ))
  )

  all_listings  <- list()
  current_since <- start_date
  prev_cursor   <- NULL
  run           <- 0

  repeat {
    run   <- run + 1
    page  <- 1
    batch <- list()
    hit_limit <- FALSE

    repeat {
      payload <- modifyList(base_payload, list(
        listedSince = current_since,
        sort        = list(sortKey = "DateListed", direction = "Ascending"),
        pageSize    = page_size,
        pageNumber  = page
      ))

      r <- tracker$post(
        paste0(PROXY_BASE, "/v1/listings/residential/_search"),
        json_body = payload
      )

      if (resp_status(r) == 400 && grepl("Cannot page beyond 1000", resp_body_string(r))) {
        hit_limit <- TRUE
        break
      }
      if (resp_status(r) != 200) {
        cat("      [", suburb, "] HTTP ", resp_status(r),
            " on run ", run, " page ", page, "\n", sep = "")
        return(all_listings)
      }

      groups <- resp_body_json(r, simplifyVector = FALSE)
      for (g in groups) {
        raw <- g$listings
        if (is.null(raw) || length(raw) == 0) raw <- g$listing
        if (is.null(raw) || length(raw) == 0) next
        if (is.null(names(raw))) batch <- c(batch, raw) else batch <- c(batch, list(raw))
      }

      hdr <- resp_header(r, "x-pagination-pagesize")
      actual_page_size <- if (is.null(hdr)) page_size else as.integer(hdr)
      if (length(groups) < actual_page_size) break
      page <- page + 1
    }

    for (item in batch) {
      id <- field(item, "id")
      if (!is.na(id)) all_listings[[as.character(id)]] <- item
    }

    if (!hit_limit || length(batch) == 0) break

    dates <- vapply(batch, \(item) substr(field(item, "dateListed"), 1, 10), character(1))
    dates <- dates[!is.na(dates)]
    if (length(dates) == 0) break
    cursor <- max(dates)
    if (!is.null(prev_cursor) && cursor == prev_cursor) break
    prev_cursor   <- cursor
    current_since <- cursor
  }

  all_listings
}

cat("fetch_suburb_listings defined.\n")
```

```{r extract-fields}
extract_fields <- function(item) {
  # Pull the key fields out of a raw listing record into a flat row.
  #
  # API listing records are deeply nested lists. field() walks that nesting and
  # returns NA when any level is missing, so every row comes out the same shape.
  #
  # item: one listing record from the API response.
  # Returns: a one-row tibble with the key fields.

  price <- field(item, "soldData", "soldPrice")
  if (is.na(price)) price <- field(item, "priceDetails", "price")

  tibble(
    listing_id    = as.character(field(item, "id")),
    suburb        = field(item, "propertyDetails", "suburb"),
    property_type = field(item, "propertyDetails", "propertyType"),  # e.g. 'House'
    bedrooms      = field(item, "propertyDetails", "bedrooms"),
    date_listed   = substr(field(item, "dateListed"), 1, 10),        # keep only YYYY-MM-DD
    date_sold     = substr(field(item, "soldData", "soldDate"), 1, 10),
    sold_price    = price,
    sale_method   = field(item, "soldData", "saleMethod")  # e.g. 'SoldByAuction'
  )
}

cat("extract_fields defined.\n")
```

------------------------------------------------------------------------

## The Checkpoint-Aware Extraction Loop

Here is what the loop does, step by step:

1.  **On startup:** load the checkpoint file if it exists. If no file
    exists, start with empty progress.
2.  **For each suburb:** check if it is already in the `completed` list.
    If yes, print "already done, skipping" and move on. If no, fetch it.
3.  **After each suburb:** save the updated checkpoint to disk.
4.  **If interrupted:** catch the interrupt, save one final checkpoint,
    and print instructions for resuming.

### Configure your suburb list and start date

Edit the chunk below to set up your actual study area. The suburb name
must be spelled exactly as it appears on the Domain website. The start
date is in `YYYY-MM-DD` format.

> **Note:** There is a start date but no end date. The extraction
> retrieves all records from `START_DATE` up to the most recent listing
> available at the time you run it. If you need to limit your study to a
> specific period, you will need to filter the resulting table by date
> after the extraction completes.

```{r configure-suburbs}
# Edit this chunk to define your study area.
# Each entry is suburb name, state code, postcode.
SUBURBS_TO_FETCH <- list(
  list("Carlton",     "VIC", "3053"),
  list("Fitzroy",     "VIC", "3065"),
  list("Collingwood", "VIC", "3066"),
  list("Richmond",    "VIC", "3121"),
  list("Brunswick",   "VIC", "3056"),
  list("Northcote",   "VIC", "3070"),
  list("Abbotsford",  "VIC", "3067"),
  list("Prahran",     "VIC", "3181"),
  list("St Kilda",    "VIC", "3182"),
  list("South Yarra", "VIC", "3141")
)

# Only include listings where the listing date is on or after this date
START_DATE <- "2022-01-01"

cat("Suburbs to fetch:", length(SUBURBS_TO_FETCH), "\n")
cat("Start date:", START_DATE, "\n\n")
cat("Suburb list:\n")
for (entry in SUBURBS_TO_FETCH) {
  cat("  ", entry[[1]], " ", entry[[3]], " (", entry[[2]], ")\n", sep = "")
}
```

### Run the extraction

**This chunk will make real API calls and spend real credits.** Before
running it:

-   Confirm the suburb list and start date above are correct.
-   Check your remaining credit balance on the AURIN dashboard.

The chunk will print progress as it goes. If you press the Stop button
in RStudio (or close your laptop), the checkpoint is saved and you can
re-run this chunk to continue from where you stopped.

```{r run-extraction}
# Load any existing checkpoint (returns empty placeholders if none exists)
cp        <- load_checkpoint(CHECKPOINT_FILE)
completed <- cp$completed
results   <- cp$results
cat("\n")

tryCatch({

  for (entry in SUBURBS_TO_FETCH) {
    suburb   <- entry[[1]]
    state    <- entry[[2]]
    postcode <- entry[[3]]

    key <- paste(suburb, postcode)  # a label for this suburb used in the checkpoint

    if (key %in% completed) {
      # This suburb is already done, skip it without spending any credits
      cat("  [", key, "] already done -- skipping.\n", sep = "")
      next
    }

    cat("  Fetching ", key, "...\n", sep = "")
    suburb_results <- fetch_suburb_listings(
      suburb, state, postcode, start_date = START_DATE, tracker = tracker
    )

    # Add this suburb's listings to the running total.
    # Assigning by name means a listing already present is overwritten, not duplicated.
    results[names(suburb_results)] <- suburb_results

    # Mark this suburb as done
    completed <- c(completed, key)

    # Save progress to disk immediately after each suburb completes
    save_checkpoint(CHECKPOINT_FILE, completed, results)

    cat("  [", key, "] done: ", format(length(suburb_results), big.mark = ","),
        " listings.\n", sep = "")
  }

  # This runs only if the loop completed without interruption
  tracker$checkpoint("Full extraction")
  cat("\nExtraction complete: ", length(completed), " suburbs, ",
      format(length(results), big.mark = ","), " listings.\n", sep = "")

}, interrupt = function(cnd) {
  # This block runs if you press the Stop button in RStudio
  cat("\nStopped by user. Saving progress...\n")
  save_checkpoint(CHECKPOINT_FILE, completed, results)
  cat("Progress saved: ", length(completed), "/", length(SUBURBS_TO_FETCH),
      " suburbs done.\n", sep = "")
  cat("Re-run this chunk to continue from where you stopped.\n")
})
```

------------------------------------------------------------------------

## Demonstration: Simulating a Failure and Recovering

The next few chunks show exactly what happens when an extraction fails
partway through. We deliberately trigger an error at suburb 5, inspect
the checkpoint file that was saved, and then resume.

**You do not need to run these chunks in a real extraction.** They are
here so you can see the recovery process working before you rely on it
for important data.

### Step 1: Run until the triggered failure

```{r demo-failure}
# DEMONSTRATION: clear the checkpoint and run until a deliberate error

# Clear any existing checkpoint so the demonstration starts from scratch
if (file.exists(CHECKPOINT_FILE)) {
  file.remove(CHECKPOINT_FILE)
  cat("Existing checkpoint cleared for demonstration.\n")
}

# Use a separate tracker so demonstration calls are counted separately from
# the real extraction above
demo_tracker <- make_tracker()

demo_completed <- character(0)
demo_results   <- list()

tryCatch({

  for (i in seq_along(SUBURBS_TO_FETCH)) {
    entry    <- SUBURBS_TO_FETCH[[i]]
    suburb   <- entry[[1]]
    state    <- entry[[2]]
    postcode <- entry[[3]]
    key      <- paste(suburb, postcode)

    if (key %in% demo_completed) next

    # DELIBERATELY TRIGGER A FAILURE at the 5th suburb
    if (i == 5) {
      # stop() raises an error, simulating a crash or network failure
      stop("Simulated failure at suburb ", i, ": ", key)
    }

    cat("  [", i, "/", length(SUBURBS_TO_FETCH), "] Fetching ", key, "...\n", sep = "")
    suburb_results <- fetch_suburb_listings(
      suburb, state, postcode, start_date = START_DATE, tracker = demo_tracker
    )
    demo_results[names(suburb_results)] <- suburb_results
    demo_completed <- c(demo_completed, key)
    save_checkpoint(CHECKPOINT_FILE, demo_completed, demo_results)
    cat("  [", key, "] done.\n", sep = "")
  }

}, error = function(e) {
  cat("\nFAILURE:", conditionMessage(e), "\n")
  cat("Checkpoint contains", length(demo_completed), "completed suburbs.\n")
  cat("In a real scenario, this would be a network error or a crashed session.\n")
})
```

### Step 2: Inspect the checkpoint file

The chunk below reads the checkpoint file and shows what was saved
before the failure.

```{r inspect-checkpoint}
if (file.exists(CHECKPOINT_FILE)) {
  checkpoint_data <- jsonlite::read_json(CHECKPOINT_FILE, simplifyVector = FALSE)

  cat("Checkpoint file size:", format(file.size(CHECKPOINT_FILE), big.mark = ","), "bytes\n")
  cat("Last saved:          ",
      if (is.null(checkpoint_data$last_updated)) "unknown" else checkpoint_data$last_updated, "\n")
  cat("Completed suburbs:   ", paste(unlist(checkpoint_data$completed), collapse = ", "), "\n")
  cat("Listings saved:      ", format(length(checkpoint_data$results), big.mark = ","), "\n\n")
  cat("These suburbs will be SKIPPED when we resume.\n")
} else {
  cat("No checkpoint file found.\n")
}
```

### Step 3: Resume

The chunk below runs the same extraction loop. Suburbs already in the
checkpoint are skipped immediately with a message. Only the remaining
suburbs are fetched.

```{r demo-resume}
# Load the checkpoint from before the failure
cp_resume       <- load_checkpoint(CHECKPOINT_FILE)
resume_completed <- cp_resume$completed
resume_results   <- cp_resume$results
skipped_at_start <- length(resume_completed)
cat("\n")

tryCatch({

  for (entry in SUBURBS_TO_FETCH) {
    suburb   <- entry[[1]]
    state    <- entry[[2]]
    postcode <- entry[[3]]
    key      <- paste(suburb, postcode)

    if (key %in% resume_completed) {
      cat("  [", key, "] already done -- skipping.\n", sep = "")  # no credit spent
      next
    }

    cat("  Fetching ", key, "...\n", sep = "")
    suburb_results <- fetch_suburb_listings(
      suburb, state, postcode, start_date = START_DATE, tracker = tracker
    )
    resume_results[names(suburb_results)] <- suburb_results
    resume_completed <- c(resume_completed, key)
    save_checkpoint(CHECKPOINT_FILE, resume_completed, resume_results)
    cat("  [", key, "] done.\n", sep = "")
  }

  tracker$checkpoint("Resume run")
  cat("\nResume complete.\n")
  cat("  Suburbs skipped (already in checkpoint):", skipped_at_start, "\n")
  cat("  Suburbs fetched in this run:            ",
      length(resume_completed) - skipped_at_start, "\n")
  cat("  Total listings collected:               ",
      format(length(resume_results), big.mark = ","), "\n")

}, interrupt = function(cnd) {
  cat("Stopped. Progress saved.\n")
  save_checkpoint(CHECKPOINT_FILE, resume_completed, resume_results)
})
```

------------------------------------------------------------------------

## Building the Final Dataset

Once all suburbs are done, load the checkpoint and build a single
combined table. This table can be saved as a CSV file that you can open
in Excel, Python, QGIS, or any other analysis tool.

```{r build-final}
# Load the final checkpoint
cp_final       <- load_checkpoint(CHECKPOINT_FILE)
final_results  <- cp_final$results

if (length(final_results) > 0) {
  # Build a table: one row per listing, using extract_fields to flatten each record
  df_final <- final_results |>
    map(extract_fields) |>
    bind_rows()

  # Convert date columns to proper dates for easier filtering.
  # as.Date() with an explicit format returns NA for anything unparseable
  # rather than stopping with an error.
  df_final <- df_final |>
    mutate(
      date_sold   = as.Date(date_sold,   format = "%Y-%m-%d"),
      date_listed = as.Date(date_listed, format = "%Y-%m-%d")
    )

  cat("Final dataset: ", format(nrow(df_final), big.mark = ","),
      " listings across ", n_distinct(df_final$suburb), " suburbs\n\n", sep = "")
  cat("Records per suburb:\n")
  print(df_final |> count(suburb, sort = TRUE), n = Inf)
  cat("\n")
  knitr::kable(head(df_final, 5))
} else {
  cat("No results in checkpoint. Run the extraction loop above first.\n")
}
```

### Export to CSV

A CSV file is a plain-text spreadsheet that Excel and other tools can
open. Run the chunk below to save your dataset. The file will appear in
the same folder as this notebook (`training-materials-r/phase-2/`).

```{r export-csv}
# Change the filename to something meaningful for your study
# If you save somewhere other than this folder, give the full path, using
# forward slashes (/) or doubled backslashes (\\). A pasted Windows path with
# single backslashes will not work.
output_filename <- "inner_melbourne_sold_listings.csv"

if (exists("df_final") && nrow(df_final) > 0) {
  write_csv(df_final, output_filename)
  cat("Saved:  ", output_filename, "\n")
  cat("Rows:   ", format(nrow(df_final), big.mark = ","), "\n")
  cat("Columns:", paste(names(df_final), collapse = ", "), "\n\n")
  cat("You can now open this file in Excel or import it into Python, QGIS, or STATA.\n")
} else {
  cat("No data to save. Run the dataset-building chunk above first.\n")
}
```

------------------------------------------------------------------------

## What If Something Goes Wrong?

**"No checkpoint file found" on startup:** This is normal on the first
run. The loop will start from the beginning.

**A suburb returns zero listings:** Check the suburb name and postcode
spelling. The suburb name must match Domain exactly, including
capitalisation. For example, "St Kilda" not "st kilda".

**The final row count seems too low:** Run a density probe (from
Notebook 1) on a few suburbs to check the expected counts, then compare
to what is in `df_final`.

**How to start completely fresh:** Delete the checkpoint file at
`checkpoints/extraction_checkpoint.json` and re-run the extraction loop.
You can delete it from RStudio's Files pane or from your operating
system's file manager.

**Authentication failure:** Check your `.env` file in the main
`domain_api` folder.

------------------------------------------------------------------------

## What's Next: Notebook 4

You can now handle the two most common challenges in large-scale
listings extractions: areas with more than 1,000 records (cursor
advancement) and runs that can be interrupted without losing progress
(checkpoint recovery).

**Notebook 4** covers spatial querying. Instead of searching by suburb
name, you provide a geographic boundary file (an SA2, LGA, or any custom
shape) and ask for all listings whose property coordinates fall inside
it. The same cursor advancement technique from this notebook applies
equally to spatial queries.

Open `notebook-4-spatial-querying.Rmd` to continue.

------------------------------------------------------------------------

## Credit Summary

The table below shows credits consumed in the resume run only (the
second run after the simulated failure). Compare the "Suburbs fetched in
this run" count to the total number of suburbs to confirm checkpoint
skipping worked correctly.

```{r credit-summary}
tracker$summary()
```
