---
title: "Notebook 1: The Listings Endpoint"
output:
  html_document:
    toc: true
    toc_depth: 2
editor_options: 
  markdown: 
    wrap: 72
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(message = FALSE, warning = FALSE)
```

## What this notebook covers

The listings endpoint is one of the main data sources on the Domain API.
It returns individual property records, one per property, with fields
like address, price, listing date, property type, and number of
bedrooms.

This notebook teaches you:

1.  How the listings endpoint works and how to structure a data access
    request.
2.  How to apply filters (listing type, property type, date range).
3.  How to detect the total record count with a density probe.
4.  How to retrieve all records page by page for areas with up to 1,000
    listings.
5.  How to save your results to a CSV file.

For requests with more than 1,000 listings, a proper tutorial is
provided in Notebook 3.

**By the end** you will have a complete dataset for a Melbourne suburb
stored in a table and saved as a CSV file.

------------------------------------------------------------------------

## Before You Start

**If you have already completed Notebook 0**, your packages, `.env`
file, and connection are already set up. Skip to the *Key Terms* section
below.

If this is your first exposure to Domain API, complete
`notebook-0-getting-started.Rmd` before this notebook. It covers package
installation, creating the `.env` credentials file, and making a test
call to confirm your connection works.

------------------------------------------------------------------------

## Key Terms

**API (Application Programming Interface):** A way for your computer to
ask another computer for data over the internet. Think of it as placing
a phone order at a restaurant rather than walking in.

**Endpoint:** A specific address within an API that handles one type of
request. This notebook uses the residential listings search endpoint.

**Credit:** One unit of API usage. Every request costs 1 credit,
regardless of how many records it returns. Your AURIN account has 1,000
credits per month.

**Record:** One row of data. In this notebook, one property listing.

**POST request:** The request method used by the listings endpoint. You
send a JSON body describing your search criteria, and the server
responds with matching records.

**Pagination:** When a large set of results is split across multiple
pages. You request page 1, then page 2, and so on.

**JSON:** A text format for storing structured data. The API sends
responses and accepts requests in JSON format. In R, a JSON object
arrives as a *named* list and a JSON array as an *unnamed* list.

**Tibble:** A table of data in R, similar to an Excel spreadsheet. Rows
are listings, columns are fields (suburb, price, date, and so on). It is
the modern version of R's built-in `data.frame`.

------------------------------------------------------------------------

## The Listings Endpoint: What It Returns

The endpoint address is:

```         
POST /v1/listings/residential/_search
```

You send it a JSON body describing your search criteria. It responds
with a list of property records.

**Key fields in each record:**

| Field path | Description |
|------------------------------------|------------------------------------|
| `id` | Unique listing identifier |
| `listingType` | `Sold` or `Rent` |
| `dateListed` | Date the listing appeared on Domain |
| `soldData.soldPrice` | Sale price (sold listings only) |
| `propertyDetails.suburb` | Suburb name |
| `propertyDetails.propertyType` | Property type (see note below) |
| `propertyDetails.bedrooms` | Number of bedrooms |
| `propertyDetails.latitude` | Latitude coordinate (used in Notebook 4 for spatial queries) |
| `propertyDetails.longitude` | Longitude coordinate |

> **Property types on this endpoint:** the listings endpoint returns a
> wide range of values here, including `House`, `ApartmentUnitFlat`,
> `Townhouse`, `Villa`, `Land`, `Rural`, and others. This is different
> from the suburb statistics endpoint in Notebook 2, which only accepts
> `House` or `Unit` as a filter. For the full list of values, see the
> *Agents & Listings API - Data Dictionary* in the metadata.

The API wraps records in group objects in its response. The `fetch_page`
function later in this notebook unpacks that structure automatically.

------------------------------------------------------------------------

## The 1,000-Record Cap: Why It Matters

Imagine you ask a librarian for every book published between 2019 and
2024 on a particular topic. The librarian hands you a pile of 1,000
books and says nothing. You take them home assuming that is all there
is. But there were actually 4,200 books, the librarian quietly held back
3,200 without any warning.

That is exactly what the Domain API does. If your query matches 4,200
records, you get the first 1,000. The remaining 3,200 are silently
dropped. No error. No warning. No note saying "we held some back."

The fix is to always ask the librarian "how many books match?" before
deciding how to retrieve them. That is the density probe.

------------------------------------------------------------------------

## Setup: Check Your Packages

Run the chunk below to confirm all required packages are installed. You
should see "All packages found. Setup OK." at the end. If any package is
missing, the chunk will tell you which one and what command to run to
install it.

```{r package-check}
needed <- c("httr2", "jsonlite", "purrr", "tibble", "dplyr", "readr")
missing <- needed[!vapply(needed, requireNamespace, logical(1), quietly = TRUE)]

if (length(missing) > 0) {
  cat("The following packages are missing:\n")
  for (pkg in missing) cat("  ", pkg, "\n")
  cat("\nRun this in the R console:\n")
  cat("  install.packages(c(", paste0('"', missing, '"', collapse = ", "), "))\n", sep = "")
  cat("Then restart R (Session menu, Restart R) and run this chunk again.\n")
} else {
  cat("All packages found. Setup OK.\n")
}
```

------------------------------------------------------------------------

## Setup: Connect to the API

The chunk below loads your credentials from the `.env` file and connects
to the AURIN proxy. It prints your username so you can confirm the right
account is being used. Your password is never printed.

**What `source("utils.R")` does:** it runs the `utils.R` helper file,
which loads your credentials and defines the functions shared across all
five notebooks, so you do not need to repeat that code here. Because
both files are in the same folder, the plain filename is all that is
needed.

```{r connect}
library(dplyr)
library(tibble)
library(purrr)
library(readr)

source("utils.R")

# Create a tracker that will count every API call we make
tracker <- make_tracker()

cat("Connected to:", PROXY_BASE, "\n")
cat("Account:     ", AURIN_USERNAME, "\n")
```

**Expected output:** Two lines. The first shows the proxy URL. The
second shows your AURIN email address. If the chunk stops with an error
about `.env`, re-read Step 2 in Notebook 0 and confirm the `.env` file
is in the main `domain_api` folder (not inside
`training-materials-r/phase-2/`). The error message prints the folder it
searched.

------------------------------------------------------------------------

## Step 1: The Density Probe

Before downloading anything, run a quick 1-credit check to find out how
many records your query would return. This is like asking "how many
books match my search?" before deciding how to retrieve them.

The probe sends a request with `pageSize = 1` (asking for just one
record). The API processes the full query and tells you the total match
count in a response header called `X-Total-Count`. The probe function
reads that header and returns the number.

We will probe two suburbs:

- **South Yarra 3141** (inner Melbourne, broad date window), expected to
  exceed 1,000
- **Williamstown 3016** (outer Melbourne, narrower window), expected to
  be under 1,000

### Define the queries

First, define the search parameters for each suburb. Read the comments
carefully, each line explains what it does. You will not spend any
credits yet.

```{r define-queries}
# Define the search for South Yarra (dense suburb, broad date window)
dense_payload <- list(
  listingType = "Sold",        # we want properties that have already sold
  listedSince = "2019-01-01",  # only include listings that appeared from this date onwards
  locations = list(list(
    state    = "VIC",
    suburb   = "South Yarra",  # suburb name, must match Domain exactly
    postCode = "3141",
    includeSurroundingSuburbs = FALSE  # do not include neighbouring suburbs
  ))
)

# Define the search for Williamstown (sparser suburb, narrower date window)
sparse_payload <- list(
  listingType = "Sold",
  listedSince = "2023-01-01",  # shorter window keeps count under 1,000
  locations = list(list(
    state    = "VIC",
    suburb   = "Williamstown",
    postCode = "3016",
    includeSurroundingSuburbs = FALSE
  ))
)

cat("Queries defined. No API calls made yet.\n")
```

> **Why `locations` is a list inside a list.** The API expects
> `locations` to be a JSON *array* of location objects, even when there
> is only one. `list(list(...))` produces `[{...}]`, which is correct.
> Writing `list(...)` on its own would produce `{...}` and the API would
> not accept it.

### Run the probe

The next chunk runs both probes. **This costs 2 credits total** (1 per
probe). The output will show the record count for each suburb.

Because this is a live API, the counts you see might be higher than the
example figures shown in this notebook, new listings are added
continuously. What matters is whether your count is above or below
1,000, not the exact number.

```{r run-probes}
# Run the density probe for the dense suburb (1 credit)
dense_count <- probe_count(dense_payload, tracker)
tracker$checkpoint("Probes")

# Run the density probe for the sparse suburb (1 credit)
sparse_count <- probe_count(sparse_payload, tracker)
tracker$checkpoint("Probes")

cat("South Yarra 3141 (from 2019): ", format(dense_count,  big.mark = ","), " records\n", sep = "")
cat("Williamstown 3016 (from 2023): ", format(sparse_count, big.mark = ","), " records\n", sep = "")
```

**What the numbers mean:**

- If a count is **1,000 or less**, simple pagination (Step 2) will
  retrieve all records in a straightforward page-by-page loop.
- If a count is **over 1,000**, simple pagination will silently miss
  records above position 1,000. Notebook 3 (Pagination Tricks) covers
  the cursor advancement technique needed for those cases.

The probe is never wasted. Even if the count turns out to be small, 1
credit to confirm completeness is far cheaper than building a study on
unknowingly incomplete data.

------------------------------------------------------------------------

## Step 2: Simple Pagination for Small Areas

When the probe count is 1,000 or fewer, a page-by-page loop retrieves
all records. Think of it like flipping through a short catalogue: you
read page 1, page 2, and so on until you reach the last page. Each page
holds up to 200 records.

The loop stops when a page comes back with fewer records than the page
size, or with no records at all. The second condition handles the case
where the total is an exact multiple of 200. Without it, the loop would
make one extra unnecessary API call.

### The `fetch_page` function

The chunk below defines a helper function that fetches one page at a
time. Read the comments to understand each line. You will not call this
function yet.

```{r fetch-page}
fetch_page <- function(base_payload, page, page_size = 200, tracker) {
  # base_payload: the search criteria (suburb, date range, listing type).
  # page:         which page number to retrieve (1 = first page).
  # page_size:    how many records per page (maximum 200).
  #
  # Returns: a list with two parts, $listings (the records) and $has_more
  #          (TRUE if more pages exist, FALSE if this was the last).

  # Add page number and page size to the query.
  # modifyList() merges two lists, with the second one winning on any shared names.
  payload <- modifyList(base_payload, list(pageSize = page_size, pageNumber = page))

  # Send the request to the API
  r <- tracker$post(
    paste0(PROXY_BASE, "/v1/listings/residential/_search"),
    json_body = payload
  )

  # If the request failed, print the error and return nothing
  if (resp_status(r) != 200) {
    cat("  Page", page, "failed: HTTP", resp_status(r), "\n")
    return(list(listings = list(), has_more = FALSE))
  }

  # Extract the listings from the response JSON.
  # The API wraps listings in groups (e.g. projects), so we unwrap them here.
  groups <- resp_body_json(r, simplifyVector = FALSE)
  listings <- list()

  for (g in groups) {
    raw <- g$listings
    if (is.null(raw) || length(raw) == 0) raw <- g$listing
    if (is.null(raw) || length(raw) == 0) next

    # A JSON array of listings arrives as an UNNAMED list; a single JSON listing
    # object arrives as a NAMED list. That is how we tell the two apart in R.
    if (is.null(names(raw))) {
      listings <- c(listings, raw)        # add a list of listings
    } else {
      listings <- c(listings, list(raw))  # add a single listing
    }
  }

  # Check if there are more pages by comparing how many groups came back
  # to the page size. If fewer came back, this was the last page.
  hdr <- resp_header(r, "x-pagination-pagesize")
  actual_page_size <- if (is.null(hdr)) page_size else as.integer(hdr)
  has_more <- length(groups) >= actual_page_size

  list(listings = listings, has_more = has_more)
}

cat("fetch_page defined.\n")
```

### The `fetch_all_simple` function

This function calls `fetch_page` in a loop until there are no more
pages. It collects all the results into one list. Run the chunk to
define it.

```{r fetch-all-simple}
fetch_all_simple <- function(base_payload, tracker) {
  # Retrieve all listings for a query that returns 1,000 or fewer total records.
  #
  # Loops through pages until no more are available. Prints progress as it goes.
  # Do NOT use this for queries that exceed 1,000 records, use fetch_all_cursor
  # from Notebook 3 instead.

  all_listings <- list()   # this list will grow as we collect each page
  page <- 1

  repeat {  # keep looping until we explicitly break out
    result <- fetch_page(base_payload, page, tracker = tracker)
    batch  <- result$listings

    all_listings <- c(all_listings, batch)  # add this page's results to the running total
    cat("  Page ", page, ": +", length(batch),
        " records | total so far: ", length(all_listings), "\n", sep = "")

    # Stop if the page was empty, or if the API signals no more pages exist.
    # The empty-batch check handles the edge case where the total record count
    # is an exact multiple of page_size (e.g. exactly 200, 400, 600 ...): in
    # that case the final real page looks "full" and has_more is TRUE, so without
    # this check the loop would make one extra credit-costing call that returns
    # nothing. Checking for an empty batch catches that and exits cleanly.
    if (length(batch) == 0 || !result$has_more) break

    page <- page + 1  # move to the next page
  }

  all_listings
}

cat("fetch_all_simple defined.\n")
```

### Run simple pagination on Williamstown

The chunk below fetches all records for Williamstown 3016 using simple
pagination. It then builds a table from the results so you can inspect
them.

**Expected output:** You should see one or more lines like "Page 1: +200
records", followed by a table showing the first five listings.

```{r fetch-williamstown}
cat("Fetching Williamstown 3016 (simple pagination)...\n")
williamstown_raw <- fetch_all_simple(sparse_payload, tracker)
tracker$checkpoint("Williamstown simple fetch")

# A listing's price lives in one of two places depending on the listing type,
# so this small helper checks the sold price first and falls back to the asking price.
sold_price_of <- function(item) {
  price <- field(item, "soldData", "soldPrice")
  if (is.na(price)) price <- field(item, "priceDetails", "price")
  price
}

# Build a table from the raw listing data.
# Each listing is a deeply nested list; we pull out the key fields here.
# field() returns NA when a field is missing, which keeps every row the same shape.
df_willi <- williamstown_raw |>
  map(\(item) tibble(
    id            = as.character(field(item, "id")),
    suburb        = field(item, "propertyDetails", "suburb"),
    property_type = field(item, "propertyDetails", "propertyType"),
    bedrooms      = field(item, "propertyDetails", "bedrooms"),
    date_listed   = substr(field(item, "dateListed"), 1, 10),  # keep only the date part
    sold_price    = sold_price_of(item)
  )) |>
  bind_rows()

cat("\nWilliamstown:", format(nrow(df_willi), big.mark = ","), "records fetched.\n")
knitr::kable(head(df_willi, 5))
```

### What else is in each record?

The table above only extracts six fields, but each listing contains much
more. A few fields worth knowing about:

| Field path | Description |
|------------------------------------|------------------------------------|
| `soldData.soldDate` | The date the property actually sold (different from `dateListed`, which is when the listing appeared on Domain) |
| `soldData.saleMethod` | How it sold: `SoldByAuction`, `SoldByPrivateTreaty`, `SoldPriorToAuction`, `Withdrawn`, or `NotStated` |
| `propertyDetails.displayableAddress` | Full street address as a single string |
| `propertyDetails.bathrooms` | Number of bathrooms |
| `propertyDetails.carspaces` | Number of car spaces |
| `propertyDetails.landArea` | Land area in square metres |
| `propertyDetails.buildingArea` | Building area in square metres |
| `propertyDetails.features` | List of features, e.g. `AirConditioning`, `Ensuite` |
| `headline` | The listing title as it appeared on Domain |

**Why `substr(x, 1, 10)` is enough for the date:** date fields like
`dateListed` and `soldData.soldDate` come back as ISO 8601 datetime
strings (for example `2023-04-07T00:00:00`). The first 10 characters are
always the date (`2023-04-07`); the time portion is always midnight and
carries no information for sold listings. Taking the first 10 characters
strips the time and gives a clean date string.

Run the chunk below to inspect a single raw record and see the full
structure returned by the API.

```{r inspect-raw}
# Print the first raw listing record so you can see everything the API returns.
# No API call is made here, this is just inspecting data already fetched above.
if (length(williamstown_raw) > 0) {
  cat(jsonlite::toJSON(williamstown_raw[[1]], auto_unbox = TRUE, pretty = TRUE))
} else {
  cat("No records were fetched, so there is nothing to inspect.\n")
}
```

------------------------------------------------------------------------

## Step 3: Filter Your Search

The payload accepts several filter fields. The most commonly used ones
are:

| Field | Example value | Effect |
|------------------------|------------------------|------------------------|
| `listingType` | `"Sold"`, `"Sale"`, `"Rent"`, `"Share"`, `"NewHomes"` | Limit to a specific listing category (see note below) |
| `propertyTypes` | array of property type values | Limit to specific property types (see note below) |
| `minBedrooms` | `2` | Only listings with at least this many bedrooms |
| `maxBedrooms` | `4` | Only listings with at most this many bedrooms |
| `listedSince` | `"2022-01-01"` | Only listings that appeared from this date onwards |

> **`listingType` values:** `Sold` returns completed sales (what most
> research uses). `Sale` returns properties currently listed for sale
> but not yet sold. `Rent` returns rental listings. `Share` returns
> share accommodation. `NewHomes` returns new home listings. For the
> full list of filter fields and allowed values, see the *Agents &
> Listings API - Data Dictionary* in the
> `metadata/data dictionary (from domain)/` folder.

> **`propertyTypes` filter values:** the API returns property types in
> PascalCase (e.g. `ApartmentUnitFlat`, `Townhouse`, `House`). See the
> full list in the response field table in the previous section. Whether
> the filter accepts these same values, or different ones, is not
> documented in the schema. Check the *Agents & Listings API - Data
> Dictionary* for confirmed filter values before using this field, and
> verify your results against your probe count.

The chunk below adds a bedroom filter to the Williamstown query and
shows how the record count changes. Filtering costs the same as an
unfiltered probe (1 credit per check).

```{r filtered-probe}
# Add a bedroom filter to the Williamstown search.
# modifyList() starts with the same criteria as before and adds the two new fields.
filtered_payload <- modifyList(sparse_payload, list(
  minBedrooms = 2,   # only properties with at least 2 bedrooms
  maxBedrooms = 4    # only properties with at most 4 bedrooms
))

# Check how many listings match the filtered criteria (1 credit)
filtered_count <- probe_count(filtered_payload, tracker)
tracker$checkpoint("Filtered probe")

cat("Williamstown (all bedrooms):   ", format(sparse_count,   big.mark = ","), "records\n")
cat("Williamstown (2 to 4 bedrooms):", format(filtered_count, big.mark = ","), "records\n\n")
cat("Excluded:", format(sparse_count - filtered_count, big.mark = ","),
    "records (studios, 1-bed, and 5-bed-plus properties)\n")
```

------------------------------------------------------------------------

## Checking Your Work

Compare the number of records you fetched against the probe count from
Step 1. They should be close. A small difference (a few records) is
normal because new listings can appear between the probe and the full
fetch.

A large difference (more than 10%) suggests the date window in the
payload changed between the probe and the fetch, or that filters were
applied inconsistently.

```{r check-work}
# Compare the probe count to the actual fetch count
cat(sprintf("Probe count (from Step 1):    %6s\n", format(sparse_count,   big.mark = ",")))
cat(sprintf("Fetched count:                %6s\n", format(nrow(df_willi), big.mark = ",")))
cat(sprintf("Difference:                   %6s  (a small number is expected)\n",
            format(abs(sparse_count - nrow(df_willi)), big.mark = ",")))
cat("\n")

# Check for duplicate records (there should be none)
duplicates <- sum(duplicated(df_willi$id))
cat("Duplicate listing IDs:", duplicates, " (expected: 0)\n\n")

cat("Date range covered:\n")
cat("  Earliest listing:", min(df_willi$date_listed, na.rm = TRUE), "\n")
cat("  Latest listing:  ", max(df_willi$date_listed, na.rm = TRUE), "\n")
```

------------------------------------------------------------------------

## Saving Your Results

Once you have a table, save it as a CSV file. A CSV is a plain-text
spreadsheet that Excel and other tools can open. Run the chunk below to
save the Williamstown dataset.

> **Save early, save often.** Data fetched from the API only exists in
> memory while the R session is running. If R crashes, you restart the
> session, or your computer shuts down, that data is gone and you will
> need to call the API again, spending credits you have already used.
> Get into the habit of saving to a CSV file immediately after every
> fetch, before doing any further analysis.

```{r save-csv}
# Save the dataset to a CSV file.
# write_csv does not write row numbers, which is what you want.
# If you save somewhere other than this folder, give the full path, using
# forward slashes (/) or doubled backslashes (\\). A pasted Windows path with
# single backslashes may not work.
output_filename <- "williamstown_sold_listings.csv"
write_csv(df_willi, output_filename)

cat("Saved:  ", output_filename, "\n")
cat("Rows:   ", format(nrow(df_willi), big.mark = ","), "\n")
cat("Columns:", paste(names(df_willi), collapse = ", "), "\n\n")
cat("You can open this file in Excel or import it into Python, QGIS, or STATA.\n")
```

------------------------------------------------------------------------

## What If Something Goes Wrong?

**An error about `.env` when loading credentials:** The `.env` file is
missing or in the wrong location. It must be in the main `domain_api`
folder, not inside `training-materials-r/phase-2/`. Check that the file
name starts with a dot and has no other extension (`.env.txt` will not
work). The error message prints the folder it searched.

**Probe returns 0 or the fetch returns an empty table:** The suburb name
or postcode may be incorrect. Domain's website shows the correct
spelling. Verify that `suburb` and `postCode` in the payload match
exactly, including capitalisation. For example, "south yarra" will not
work; it must be "South Yarra".

**The fetch count is much lower than the probe count:** The probe and
full fetch were run far apart in time, and new listings appeared between
them. A difference of more than 10% may also indicate that the date
window in the payload changed between the probe and the fetch. Re-run
the probe to confirm.

**The probe returns more than 1,000 records:** Simple pagination will
silently miss records above position 1,000. See Notebook 3 (Pagination
Tricks) for the cursor advancement technique that handles this case.

------------------------------------------------------------------------

## What's Next: Notebook 2

You can now query the listings endpoint, apply filters, retrieve all
pages for areas with up to 1,000 records, and save the results to a CSV
file.

**Notebook 2** covers a completely different endpoint: aggregated market
statistics. Instead of individual property records, it returns one row
per quarter, summarising the median sale price, the number of properties
sold, and average days on market across an entire suburb. One call
retrieves up to 11 years of quarterly history for the same cost as a
single listings probe.

Open `notebook-2-suburb-statistics.Rmd` to continue.

------------------------------------------------------------------------

## Credit Summary

The table below shows how many API credits were consumed in each section
of this notebook. Each row corresponds to a checkpoint label you saw
printed during the run.

Credits reset to 1,000 on the first of each calendar month. You can
check your remaining balance on the AURIN dashboard. There is no
programmatic way to check the balance, dashboard checks are a required
part of the workflow before any large extraction.

```{r credit-summary}
tracker$summary()
```
