---
title: "Notebook 0: Getting Started"
output:
  html_document:
    toc: true
    toc_depth: 2
editor_options: 
  markdown: 
    wrap: 72
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(message = FALSE, warning = FALSE)
```

This notebook has one job: get your computer connected to the Domain API
and pull back real data.

By the end, you will have run a successful query and seen live property
market statistics for a Melbourne suburb. Everything in Notebooks 1 to 4
builds on exactly what you do here.

**No prior programming experience is assumed** beyond being able to open
RStudio and run a code chunk.

------------------------------------------------------------------------

## What You Will Need

Check that you have these four things before running anything:

- **R, version 4.1 or later.** The notebooks use R's native pipe (`|>`)
  and the short lambda syntax (`\(x)`), both of which need 4.1 or newer.
  Type `R.version.string` in the console to check. If you do not have R
  yet, the [Data Access Guide](../phase-1/01-data-access-guide.md) has a
  step-by-step setup checklist at the bottom.
- **RStudio** (recommended). It gives you a Run button for each chunk
  and a Knit button to turn this notebook into an HTML report. You can
  also run these files from VS Code or the plain R console.
- **Your AURIN username and password.** These are the same credentials
  you use to log in at [data.aurin.org.au](https://data.aurin.org.au).
  If you have not signed the Domain API access agreement yet, do that
  first; the Data Access Guide walks you through it.
- **`utils.R` in the same folder as this notebook.** This is a helper
  file that handles authentication and tracks your API credit usage. If
  you downloaded this notebook on its own, you will also need to
  download `utils.R` from the same source and place it in the same
  folder. If you are working from the full project folder, it is already
  there.

------------------------------------------------------------------------

## Step 1: Install the Required Packages

Packages are add-ons that give R extra abilities. You only need to
install them once.

The easiest way is to run the `install-packages.R` file that sits next
to this notebook. In RStudio, open it and click **Source**. From a
terminal, run:

```         
Rscript install-packages.R
```

It takes a few minutes the first time. The packages it installs are:

- `httr2`: sends questions to the API and receives answers back
- `jsonlite`: reads the API's answers, which arrive in a format called
  JSON
- `dplyr`, `tibble`, `purrr`: organise data into neat tables
- `readr`: saves your results to a CSV file
- `ggplot2`, `leaflet`: draw the charts and maps in later notebooks

If a package is already installed it is skipped, so it is safe to
re-run.

Then run the chunk below to confirm everything is in place.

```{r package-check}
# Run this chunk first.
# If anything is missing, the output will tell you exactly what to install.

needed <- c("httr2", "jsonlite", "purrr", "tibble", "dplyr", "readr")
missing <- needed[!vapply(needed, requireNamespace, logical(1), quietly = TRUE)]

if (length(missing) > 0) {
  cat("Some packages are missing:", paste(missing, collapse = ", "), "\n\n")
  cat("Run this in the R console:\n\n")
  cat("  install.packages(c(", paste0('"', missing, '"', collapse = ", "), "))\n\n", sep = "")
  cat("Or open install-packages.R and click Source. Then re-run this chunk.\n")
} else {
  cat("All packages found. You are good to go.\n")
}
```

------------------------------------------------------------------------

## Step 2: Save Your Credentials

Your AURIN username and password need to be available to your code, but
you should never type them directly into a notebook. Notebooks can
accidentally get shared or uploaded to GitHub.

Instead, you store them in a plain text file called `.env` (the dot at
the start is intentional, there is no `.txt` extension). This file stays
on your computer and is not included in your notebook, so it will not be
shared if you send the notebook to someone else.

**Where to create it:** in the same folder as this notebook, or any
folder above it. A good practice is to keep it in your project's
top-level folder so all your notebooks can share the one file.

**How to create it:**

1.  Open the folder where you want to keep the file
2.  Create a new plain text file called `.env`
    - On **Windows**: open Notepad, then use File, Save As and choose
      "All Files" as the file type. Name it `.env`.
    - On **Mac**: open TextEdit, go to Format, Make Plain Text, then
      save as `.env`.
    - In **RStudio**: File, New File, Text File, then save it as `.env`.
3.  Paste these two lines into the file, replacing the example values
    with your real AURIN credentials:

```         
AURIN_USERNAME=your.email@university.edu.au
AURIN_PASSWORD=your_aurin_password
```

4.  Save and close the file.

> **If you are using Git:** add `.env` to your `.gitignore` file so it
> is never accidentally committed and uploaded to GitHub.

------------------------------------------------------------------------

## Step 3: Connect to the API

Think of this like signing in to a library. You show your card once at
the start and then you can borrow books freely for the rest of your
visit.

The notebooks use a helper file called `utils.R` that handles two
things: reading your credentials from the `.env` file, and counting how
many API credits you use. It must be in the same folder as this notebook
(see *What You Will Need* above).

Running the chunk below will:

1.  Read your credentials from the `.env` file
2.  Set up a connection to the Domain API through the AURIN proxy
3.  Print your account name so you can confirm the right credentials
    were loaded

You need to do this once every time you open the notebook.

You will see output similar to this, but with your own email address:

```         
Connected to: https://domain.api.aurin.org.au
Logged in as: your.email@university.edu.au

Setup looks good. Ready to make your first call.
```

```{r connect}
# source() runs another R file and makes its functions available here.
# utils.R reads your .env file automatically when it is sourced.
source("utils.R")

# The tracker does two things:
#   1. Adds your credentials to every request automatically
#   2. Keeps count of how many credits you have used this session
tracker <- make_tracker()

cat("Connected to:", PROXY_BASE, "\n")
cat("Logged in as:", AURIN_USERNAME, "\n\n")
cat("Setup looks good. Ready to make your first call.\n")
```

> **If this chunk stops with an error** saying
> `AURIN_USERNAME / AURIN_PASSWORD not found in .env`, your `.env` file
> is missing or in the wrong place. The error message prints the folder
> it searched, so you can see exactly where to put the file. See the
> Troubleshooting section at the bottom.

------------------------------------------------------------------------

## Step 4: Make Your First API Call

We are going to ask the Domain API for one quarter (3 months) of market
statistics for Carlton, VIC.

Think of it like this: your code sends a question to Domain's server.
The server checks your credentials, looks up the data, and sends the
answer back. The whole thing takes about one second.

We are asking for:

- **Suburb:** Carlton, VIC (postcode 3053)
- **Property type:** Houses
- **Time period:** the most recent quarter only

**This will cost 1 credit.** Run the chunk below.

```{r first-call}
# The URL tells the API which suburb we want.
# Format: /v2/suburbPerformanceStatistics/{state}/{suburb}/{postcode}
url <- paste0(PROXY_BASE, "/v2/suburbPerformanceStatistics/VIC/Carlton/3053")

# These parameters say what kind of data we want
params <- list(
  propertyCategory = "House",   # "House" or "Unit"
  periodSize       = "quarters", # group data into 3-month periods
  totalPeriods     = 1           # just the most recent period for this test
)

# Send the request and store the response
response <- tracker$get(url, params = params)
tracker$checkpoint("First test call")

# Check the status code: 200 means success
status <- resp_status(response)
cat("Status:", status, "\n")

if (status == 200) {
  body <- resp_body_string(response)
  cat("Data received:", format(nchar(body), big.mark = ","), "characters\n\n")
  cat("It worked. Run the next chunk to see the actual numbers.\n")
} else if (status == 401) {
  cat("Your credentials were not accepted.\n")
  cat("Check AURIN_USERNAME and AURIN_PASSWORD in your .env file.\n")
} else if (status == 403) {
  cat("Access denied.\n")
  cat("Either the Domain API access agreement is not signed,\n")
  cat("or your monthly credits ran out.\n")
  cat("Log in to data.aurin.org.au and check: Manage Access -> API Access.\n")
} else {
  cat("Unexpected response:", substr(resp_body_string(response), 1, 300), "\n")
}
```

------------------------------------------------------------------------

## Step 5: Look at the Data

The API sent back a chunk of text in a format called JSON. Think of JSON
as a structured list of labelled values, a bit like a form that has been
filled in.

R reads JSON as a nested list. The chunk below digs into it and prints
the numbers in plain English.

You will see output similar to this, but the figures will reflect the
most recent quarter available at the time you run it:

```         
Carlton, VIC -- most recent quarter: 2026, month 3

  Median sale price:  $1,305,000
  Properties sold:    18
  Days on market:     not reported
```

"Not reported" means there were not enough sales that quarter for the
API to publish a reliable figure.

```{r read-data}
# Parse the raw response text into an R list.
# simplifyVector = FALSE keeps the nested structure, which is easier to navigate.
data <- resp_body_json(response, simplifyVector = FALSE)

# Dig into the structure to find the most recent quarter
entries <- data$series$seriesInfo

if (length(entries) == 0) {
  cat("The response came back empty.\n")
  cat("This usually means the suburb name or postcode was wrong.\n")
  cat("Carlton / 3053 should always return data -- re-check the connection chunk above.\n")
} else {
  latest <- entries[[length(entries)]]  # last entry = most recent quarter
  year   <- latest$year
  month  <- latest$month

  # field() returns NA instead of NULL when the API did not report a value,
  # which is what makes the checks below straightforward.
  median_price   <- field(latest, "values", "medianSoldPrice")
  number_sold    <- field(latest, "values", "numberSold")
  days_on_market <- field(latest, "values", "daysOnMarket")

  cat("Carlton, VIC -- most recent quarter:", year, ", month", month, "\n\n")

  # NA means there were not enough sales that quarter for the API to report a number
  if (!is.na(median_price)) {
    cat("  Median sale price:  $",
        formatC(round(median_price), format = "d", big.mark = ","), "\n", sep = "")
  } else {
    cat("  Median sale price:  not reported this quarter\n")
  }

  if (!is.na(number_sold)) {
    cat("  Properties sold:   ", number_sold, "\n")
  } else {
    cat("  Properties sold:    not reported\n")
  }

  if (!is.na(days_on_market)) {
    cat("  Days on market:    ", days_on_market, "\n")
  } else {
    cat("  Days on market:     not reported\n")
  }

  cat("\nThese numbers come directly from the live Domain API.\n")
}
```

------------------------------------------------------------------------

## About Credits

Every request you send to the API costs **1 credit**. Your AURIN account
gets **1,000 credits per month**. They reset automatically on the 1st of
each calendar month, you do not need to do anything.

1,000 sounds like a lot, but it goes quickly if you query without
planning first. For example, pulling one year of sold listings across a
single busy suburb like South Yarra can take 20 to 30 credits on its
own.

The golden rule: **design your research question before you start
querying.** The [Credit Calculator
guide](../phase-1/03-credit-calculator.md) shows you how to estimate
your total cost before running anything large.

You can check your remaining credits at any time: log in to
[data.aurin.org.au](https://data.aurin.org.au), go to **Manage Access**,
then **API Access**, and look at the Domain Access section.

The chunk below shows how many credits this session has used so far.

```{r credit-summary}
tracker$summary()
```

------------------------------------------------------------------------

## Troubleshooting

**`Error in file(filename, "r", encoding = encoding) : cannot open the connection`**
(from `source("utils.R")`) The `utils.R` file is not in the same folder
as this notebook. Download it from the same source as the notebook and
place it in the same folder, then re-run the chunk. In RStudio, check
that the working directory matches the notebook's folder: run `getwd()`
in the console. If you point R at a folder yourself with `setwd()`, note
that a pasted path may not work as is: depending on the operating system
you are using, Windows gives backslashes (`C:\Users\you\project`) and
Mac or Linux give forward slashes (`/Users/you/project`). In R, use
forward slashes (`setwd("C:/Users/you/project")`) or doubled backslashes
(`setwd("C:\\Users\\you\\project")`).

**`Error: AURIN_USERNAME / AURIN_PASSWORD not found in .env`** Your
`.env` file is missing or cannot be found. It needs to be in the same
folder as this notebook, or in a folder above it. The error message
prints the folder it searched. Also double-check the file name: it
starts with a dot (`.env`) and has no other extension, so `.env.txt`
will not work.

**`Status: 200` but the response came back empty** The suburb name or
postcode was wrong. Carlton / 3053 should always return data. If it does
not, re-run the connection chunk and try the call again.

**`Status: 401`** Your credentials were not accepted. Open the `.env`
file and check:

- No extra spaces before or after the `=`
- No extra spaces at the beginning or end of the password
- The email address matches exactly what you use to log in to AURIN

**`Status: 403`** Two possible causes:

1.  You have not signed the Domain API access agreement. Log in to
    data.aurin.org.au, then Manage Access, then My Agreements.
2.  Your monthly credits have run out. Check the dashboard.

**`there is no package called 'httr2'`** (or `jsonlite`, `purrr`,
`tibble`) A required package is not installed. Run
`Rscript install-packages.R` in your terminal, or open
`install-packages.R` in RStudio and click Source, then re-run the
package check chunk.

------------------------------------------------------------------------

## What's Next: Let's Move to Notebook 1

You have connected to the API and pulled real data back. The pattern you
just used (build a URL, send a request, check the status, read the
result) is the same pattern used in every notebook that follows.

**Notebook 1** covers the listings endpoint: the main data source on the
Domain API. It returns individual property records, one per property,
with fields like address, price, listing date, and property type. You
will learn how to structure a request, apply filters, and retrieve all
pages of results.

Open `notebook-1-listings-search.Rmd` to continue.
